### 2021-11-03 Final Doc/main.tex
Added Chapter 2 to Final Docs
Formatting

\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure
\usepackage{graphicx}
\usepackage{float}
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage[final]{pdfpages}
\usepackage{mathpazo} % Use the Palatino font by default

\usepackage[backend=biber,style=apa,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

@@

\geometry{
	paper=a4paper, % Change to letterpaper for US letter
	inner=1.5cm, % Inner margin
	outer=1.5cm, % Outer margin
	bindingoffset=0.3cm, % Binding offset
	top=0.5cm, % Top margin
	bottom=0.5cm, % Bottom margin
	%showframe, % Uncomment to show how the type block is set on the page
}

@@

\begin{titlepage}
\begin{center}
\includegraphics[scale=0.3]{nwu.png}\\[0.4cm]

@@

\include{Chapters/Chapter1}
\include{Chapters/Chapter2}

>>>>

\documentclass[
12pt, % The default document font size, options: 10pt, 11pt, 12pt
oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
onehalfspacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure

\usepackage{graphicx}
\usepackage{float}
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[final]{pdfpages}
\usepackage{mathpazo} % Use the Palatino font by default
\usepackage{changepage}
\usepackage{caption}
\usepackage[list=false]{subcaption}
\usepackage[backend=biber,style=apa,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

@@

\geometry{
	paper=a4paper, % Change to letterpaper for US letter
	inner=2.5cm, % Inner margin
	outer=2cm, % Outer margin
	%bindingoffset=0.3cm, % Binding offset
	top=2cm, % Top margin
	bottom=2.5cm, % Bottom margin
	%showframe, % Uncomment to show how the type block is set on the page
}

@@

\begin{titlepage}
\begin{center}
\includegraphics[scale=0.4]{Figures/nwu.png}\\[.4cm]

@@

\include{Chapters/Chapter1}
\include{Chapters/Chapter2}
\include{Chapters/Chapter3}
